\psalmline{First Reading}{}{Ac 3, 11-26}
\psdescr{The author of life you put to death, but God raised him from the dead.}{}
\indent A reading from the Acts of the Apostles:

As the crippled man who had been cured clung to Peter and John, all the people hurried in amazement toward them in the portico called “Solomon’s Portico.”

When Peter saw this, he addressed the people, «You children of Israel, why are you amazed at this, and why do you look so intently at us as if we had made him walk by our own power or piety? The God of Abraham, the God of Isaac, and the God of Jacob, the God of our fathers, has glorified his servant Jesus whom you handed over and denied in Pilate’s presence, when he had decided to release him. You denied the Holy and Righteous One and asked that a murderer be released to you. The author of life you put to death, but God raised him from the dead; of this we are witnesses.

And by faith in his name, this man, whom you see and know, his name has made strong, and the faith that comes through it has given him this perfect health, in the presence of all of you.

Now I know, brothers and sisters, that you acted out of ignorance, just as your leaders did; but God has thus brought to fulfillment what he had announced beforehand through the mouth of all the prophets, that his Christ would suffer. Repent, therefore, and be converted, that your sins may be wiped away, and that the Lord may grant you times of refreshment and send you the Christ already appointed for you, Jesus, whom heaven must receive until the times of universal restoration of which God spoke through the mouth of his holy prophets from of old.

For Moses said: “A prophet like me will the Lord, your God, raise up for you from among your own kin; to him you shall listen in all that he may say to you. Everyone who does not listen to that prophet will be cut off from the people.” Moreover, all the prophets who spoke, from Samuel and those afterwards, also announced these days.

You are the children of the prophets and of the covenant that God made with your ancestors when he said to Abraham, “In your offspring all the families of the earth shall be blessed.” For you first, God raised up his servant and sent him to bless you by turning each of you from your evil ways.»


\red{--–}The Word of the Lord.