\psalmline{First Reading}{}{Ac 4, 1-12}
\psdescr{There is no salvation through anyone else.}{}
\indent A reading from the Acts of the Apostles:

After the crippled man had been cured, while Peter and John were still speaking to the people, the priests, the captain of the temple guard, and the Sadducees confronted them, disturbed that they were teaching the people and proclaiming in Jesus the resurrection of the dead. They laid hands on Peter and John and put them in custody until the next day, since it was already evening. But many of those who heard the word came to believe and the number of men grew to about five thousand.

On the next day, their leaders, elders, and scribes were assembled in Jerusalem, with Annas the high priest, Caiaphas, John, Alexander, and all who were of the high-priestly class. They brought them into their presence and questioned them: «By what power or by what name have you done this?»

Then Peter, filled with the Holy Spirit, answered them: «Leaders of the people and elders: If we are being examined today about a good deed done to a cripple, namely, by what means he was saved, then all of you and all the people of Israel should know that it was in the name of Jesus Christ the Nazorean whom you crucified, whom God raised from the dead; in his name this man stands before you healed.

He is the stone rejected by you, the builders, which has become the cornerstone. There is no salvation through anyone else, nor is there any other name under heaven given to the human race by which we are to be saved.»

\red{--–}The Word of the Lord.

