\pr The Lord be with you.

\be And with your spirit.

\pr Lift up your hearts.

\be We lift them up to the Lord. 

\pr Let us give thanks to the Lord our God. 

\be It is right and just. 

\pr It is truly right and just, our duty and our salvation, at all times to acclaim you, O Lord, but on this day above all to laud you yet more gloriously, when Christ our Passover has been sacrificed. For he is the true Lamb who has taken away the sins of the world; By dying he destroyed our death; And by rising, restored our life. Therefore, overcame with paschal joy, every land, every people exults in your praise and even the heavenly Powers, with the angelic hosts, sing together the unending hymn of your glory, as they acclaim:

\be Holy, Holy, Holy Lord God of hosts.\redast Heaven and earth are full of your glory.\redast Hosanna in the highest.\redast Blessed is he who comes in the name of the Lord.\redast Hosanna in the highest.

\pr You are indeed Holy, O Lord, the fount of all holiness. Make holy, therefore, these gifts, we pray, by sending down your Spirit upon them like the dewfall, so that they may become for us the Body and Blood of our Lord Jesus Christ.

\pr At the time he was betrayed and entered willingly into his Passion, he took bread and, giving thanks, broke it, and gave it to his disciples, saying:

\vspace{1em}
\eu Take this, all of you, and eat of it, for this is My Body, which will be given up for you.
\vspace{0.8em}

\pr In a similar way, when supper was ended, he took the chalice and, once more giving thanks, he gave it to his disciples, saying:

\vspace{1em}
\eu Take this, all of you, and drink from it, for this is the chalice of My Blood, the Blood of the new and eternal covenant, which will be poured out for you and for many for the forgiveness of sins. Do this in memory of Me.
\vspace{0.8em}

\pr The mystery of faith.

\be We proclaim your Death, O Lord, and profess your Resurrection until you come again.

\pr Therefore, as we celebrate the memorial of his Death and Resurrection, we offer you, Lord, the Bread of life and the Chalice of salvation, giving thanks that you have held us worthy to be in your presence and minister to you.

\pr Humbly we pray that, partaking of the Body and Blood of Christ, we may be gathered into one by the Holy Spirit.

\pr Remember, Lord, your Church, spread throughout the world, and bring her to the fullness of charity, together with Francis our Pope and Marek our Bishop and all the clergy.

\pr Remember also our brothers and sisters who have fallen asleep in the hope of the resurrection, and all who have died in your mercy: welcome them into the light of your face.

\pr Have mercy on us all, we pray, that with the Blessed Virgin Mary, Mother of God, with the blessed Apostles, and all the Saints who have pleased you throughout the ages, we may merit to be coheirs to eternal life, and may praise and glorify you through your Son, Jesus Christ.

\pr O God, almighty Father, in the unity of the Holy Spirit, all glory and honor is yours, for ever and ever.

\be Amen.