\indent \pr In the name of the Father, and of the Son, and of the Holy Spirit.

\be Amen.

\pr The grace of our Lord Jesus Christ, and the love of God, and the communion of the Holy Spirit be with you all.

\be And with your spirit.

\pr Brothers and sisters, let us acknowledge our sins, and so prepare ourselves to celebrate the sacred mysteries.

\be I confess to almighty God\redast and to you, my brothers and sisters,\redast that I have greatly sinned,\redast in my thoughts and in my words,\redast in what I have done and in what I have failed to do,\redast through my fault, through my fault,\redast through my most grievous fault;\redast therefore I ask blessed Mary ever-Virgin,\redast all the Angels and Saints,\redast and you, my brothers and sisters,\redast to pray for me to the Lord our God.

\pr May almighty God have mercy on us, forgive us our sins, and bring us to everlasting life.

\be Amen.

\pr Lord, have mercy.\redast\be Lord, have mercy.\\
\indent\pr Christ, have mercy.\redast\be Christ, have mercy.\\
\indent\pr Lord, have mercy.\redast\be Lord, have mercy.

\be Glory to God in the highest,\redast and on earth peace to people of good will.\redast We praise you,\redast we bless you,\redast we adore you,\redast we glorify you,\redast we give you thanks for your great glory,\redast Lord God, heavenly King,\redast O God, almighty Father.\redast Lord Jesus Christ, Only Begotten Son,\redast Lord God, Lamb of God, Son of the Father,\redast you take away the sins of the world,\redast have mercy on us;\redast you take away the sins of the world,\redast receive our prayer;\redast you are seated at the right hand\redast of the Father,\redast have mercy on us.\redast For you alone are the Holy One,\redast you alone are the Lord,\redast you alone are the Most High,\redast Jesus Christ,\redast with the Holy Spirit,\redast in the glory of God the Father.\redast Amen.


\newpage \input{src/ordinario/opening_prayer_en}